---
title: "DataScienceHW1"
format: html
editor: visual
---

## Write Test

**1. What do you think being a data scientist is about?**

I believe that being a data scientist is about shaping data and identifying patterns and other insights from this data in order to support a wide variety of fields of study.

**2. What differences/similarities do you see between data scientists and statisticians?**

I believe that statistics is the foundation of data science. Therefore, I believe that statisticians do the 'behind-the-scenes' work first and then data scientists manipulate the data produced by statisticians to identify insights.

**3. How do you view yourself in relation to these two areas?**

I am an operations research analyst by trade, so I view my work as very similar to that of data scientists. I do not view myself as a statistician as I know that statistics is not my strongest area of expertise.

## Code Test

```{r}
y <- density(iris$Sepal.Length)
```

```{r}
# Determine the class of the object y
class_y <- class(y)

# Determine the type of the object y
type_y <- typeof(y)

# Determine the structure of the object y
str(y)
```

## Markdown Test

In the code chunk above, I utilized the class(), typeof(), and str() functions to, respectively, determine the class, type, and structure of the object y.

In the code chunk below, I utilized the plot() function to plot the object y. I also set the echo chunk object to false in order to hide the R code in the final, documented output.

```{r, echo=FALSE}
plot(y)
```
